Fetching Reprint Author information from the Web of Science

### 2019-10-19 analysis/003_kb_fetch_ca.Rmd
remove journal-level data

- Publisher and journal titles from Crossref
- Journal open access status provided by the Bielefeld GOLD OA list

@@

### 4. Data coding and dump

@@

>>>>

- Publisher information from Crossref
- Journal open access status provided by the ISSN GOLD OA list

@@

### 4. Data coding and dump journal-level

@@

### 5. Publisher-level data

```{r}
rp_jn <- readr::read_csv("../data/rp_jn_14_18.csv") %>%
  group_by(country_code, publication_year, publisher, oa_journal) %>%
  summarise(n_publications = sum(articles, na.rm = TRUE),
            n_journals = n_distinct(issn_l))
# export to csv and excel
readr::write_csv(rp_jn, "../data/rp_publisher_14_18.csv")
writexl::write_xlsx(rp_jn, "../data/rp_publisher_14_18.xlsx")

```

|Variable           |Description                                                                                                                                 |Source                                                                        |
|:------------------|:-------------------------------------------------------------------------------------------------------------------------------------------|:-----------------------------------------------------------------------------|
|`country_code`     |Country of affiliation corresponding author, represented as ISO 3 code                                                                      |KB Web of Science: `wos_b_2019.d_items_authors_institutions.inst_countrycode` |
|`publication_year` |Year of publication, obtained from KB Web of Science                                                                                        |KB Web of Science: `wos_b_2019.items.pubyear`                                 |
|`publisher`        |Most frequently used publisher name in terms of articles published between 2014 - 2018. If missing, the journal was not indexed in Crossref |Crossref                                                                      |
|`oa_journal`       |Is the journal publishing all articles open access without delay (full open access)?                                                        |ISSN GOLD OA List V3                                                          |
|`n_publications`   |Number of original articles and reviews published                                                                                           |Aggregate data                                                                |
|`n_journals`       |Number of distinct journals with corresponding publication output                                                                           |Aggregate data                                                                |
